---
title: "Untitled"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Hey everyone!

I worked two separate parts for this piece:
  1. Squiggly lines in the background
  2. Smearing ink blobs in the middle-

For #2, I followed Tyler Hobb's instruction. I'm just going to use the code that I worked out here: https://github.com/jiwanheo/my-aRt/blob/master/ink-smear/ink-smear.Rmd


# 1. Squiggly lines
Draw a Cosine curve, connect the 2 ends of the curve
to the left/right corners, to return a rectangle, with squiggly top.
```{r}
# We're going to draw a bunch of identical cosine curves, with 
# different offsets, so we can spread them out,
# and colour them purple/green depending on if they're on the wrong side of 0 

draw_curve <- function(n, amp, freq, val_offset) {
  len_out <- 100
  max_val <- if(val_offset < 0){15} else{-15} # This is to determine which left/right end the polygon should be based off
  nrange <- seq(1, n, length.out = len_out)  
  
  clr <- if(val_offset < 0){
    sample(c("a", "a", "a", "a", "a", "a", "b"), size = 1)} #color selection on each side of the background.
  else{
    sample(c("b", "b", "b", "b", "b", "b", "a"), size = 1)
  }
  
  df <- tibble(
    curr_pi = nrange,
    val = amp * cos(curr_pi * freq) + val_offset,
    clr = clr
  ) 
  
  # These are first and last point of the df, 
  # That connects the ends of the cos waves
  # to the bottom left/right corners
  first_corner <- tibble(
    curr_pi = 1,
    val = -max_val,
    clr = clr
  )
  
  second_corner <- tibble(
    curr_pi = len_out,
    val = -max_val,
    clr = clr
  )
  
  return(
    first_corner %>% 
      rbind(df) %>% 
      rbind(second_corner)
  )
}

call_draw_curve <- function(n_lines, n) {
  df <- tibble(
    id   = 1:n_lines,
    n    = n,
    amp  = 1.87,
    freq = 0.17
  ) %>% 
    mutate(val_offset = map_dbl(id, ~runif(n = 1, min = 1, max = 10) * sample(c(-1, 1), size = 1))) %>% 
    select(-id)
  
  df <- df %>% 
    pmap(draw_curve)
  
  df %>%
    map(~geom_polygon(data = .x, aes(x = val, y = curr_pi, fill = clr), size = 2, alpha = 0.01))
}

my_lines <- call_draw_curve(n_lines = 100, n = 100) #Draw 100 cosine curves that spans 0~100

p_ <- ggplot()

for(item in my_lines) {
  p_ <- p_ + item
}
p_ <- p_ +
  scale_fill_manual(values = c("#854784", "#3f8383")) #Spent a ton of time in this!
```

# 2. Smearing ink 
The workflow is:

- Start with a polygon. `gimmie_polygon` gives a regular polygon of n sides.
- `jutt` all sides of the polygon, out a certain amount.
- `jutt` the new sides even further, each time resulting in new sides being created.
- Do this a bunch of times for many polygons (`apply_jutt`) in layers (`soften_edges`)
- Draw them on top of each other with low opacity.

## 2.1 Base Polygon Generator

```{r}
library(tidyverse)

# Make a regular polygon. Output is in format of geom_segment
gimmie_poly <- function(n, start_x = 0, start_y = 0) {
  start <- tibble(
    id    = 1:n,
    angle = 2*pi * id/n,
    x     = cos(angle) + start_x,
    y     = sin(angle) + start_y
  )
  
  end <- start %>%
    select(id, xend = x, yend = y) %>% 
    mutate(id = ifelse(id == 1, n, (id-1) %% n)) # offsetting row id by 1 
  
  res <- start %>% 
    inner_join(end, by = "id") %>% # joining a df on itself, with offset id
    arrange(id) %>% 
    select(x, y, xend, yend) %>% 
    mutate(prot_multi = sample(c(0.4, 0.5, 0.2, 0.69, 0.42, 0.8, 0.64, 0.379))) 
    #Protrusion initial control.This controls jutting amounts.
    
  res
}
```

## 2.2 Jutting (Polygon Transformation)

1. Take an edge of a polygon
2. Pick a random point along the edge 
3. Push it out, by some amount of 
   i)  angle 
   ii) length (using prot_multi)
4. Give slight variation to prot_multi, and pass it on to the newly created edges

One iteration of this on a polygon increases the total sides by 1. 

```{r}
jutt <- function(x, y, xend, yend, prot_multi) {
  #2. Pick a random point along edge
  prop  <- rnorm(n = 1, mean = 0.5, sd = 0.5/2)
  mid_x <- (1-prop)*x + prop*xend
  mid_y <- (1-prop)*y + prop*yend
  
  #3-1. Pick a random angle to protrude off an edge
  ##### **Find the angle that makes the horizontal line btw (x,y) & (xend,yend)
  ##### **with arc tangent, and add the angle (btw 1~2pi)
  angle <- atan2(yend-y, xend-x) + rnorm(n = 1, mean = 1.5, sd = (1.5-1)/4)*pi

  #3-2. Pick the length of protrusion
  edge_len <- sqrt((xend-x)^2 + (yend-y)^2) 
  prot_amt <- rnorm(n = 1, mean = edge_len*prot_multi, sd = edge_len*prot_multi/4) #scale protrusion amt with the length of the edge and some `prot_multi` amount
  mid_xend <- mid_x + prot_amt*cos(angle) 
  mid_yend <- mid_y + prot_amt*sin(angle)

  #4. Update multiplier and pass on to the resulting edges. 
  prot_multi <- prot_multi * rnorm(1, mean = 1, sd = (1-0.98)/4)
  
  df <- tibble(
    x    = c(x, mid_xend),
    y    = c(y, mid_yend),
    xend = c(mid_xend, xend),
    yend = c(mid_yend, yend),
    prot_multi = prot_multi
  )
  
  return(df)
}
```

## 2.3 Jutting multiple polygons, multiple times

```{r}
apply_jutt <- function(dat, n) {# dat is a df containing a polygon
  for (i in 1:n) {              # we apply `jutt` n times to the df,
    dat <- dat %>%              # resulting in a polygon that has a lot more sides.
      pmap_dfr(jutt) 
  }
  return(dat)
}
```

## 2.4 Softening the edges

1. Start from a base polygon 
2. Jutt it 3 times 
3. Make a bunch of `start_pol`, and jutt them 3 more times
4. But do step 1-3 in clusters. 
   i) divide n_layers into 3, first gets 1 `base_jutt`, second gets 2, third gets 3.
   ii) then run those 3 clusters with same `post_jutt`

```{r}
soften_edges <- function(base_gon, base_jutt, n_layer, post_jutt, alpha, pol_fill, seed, start_x, start_y){
  my_params <- paste("base_gon", base_gon, "base_jutt", base_jutt, "n_layer", n_layer,"post_jutt", post_jutt, "alpha", alpha, "pol_fill", pol_fill,  "seed", seed, "start_x", start_x, "start_y", start_y)
  
  message(my_params)
  set.seed(seed)
  # Will store each layer of polygon in a list. Wuddup adv-R
  
  polygon_layers <- vector("list", n_layer) 
  for(i in seq_along(1:n_layer)) {
    
    cluster <- i%%base_jutt               #4. define clusters
    cluster <- if(cluster == 0) {base_jutt} else {cluster}

    poly <- gimmie_poly(base_gon, start_x = start_x, start_y = start_y) %>% #1. Start from base polygon
      apply_jutt(cluster)                 #2. Jutt it `cluster` times
    
    polygon_layers[[i]] <- poly       
  }
  
  polygons_softened <- polygon_layers %>%
    map(~apply_jutt(.x, post_jutt)) %>%   #3. Jutt all the polygons `base_jutt` times (same for all polygons now)
    map(~geom_polygon(data = .x, aes(x = x, y = y), alpha = alpha, fill = pol_fill, show.legend = FALSE))

  return(polygons_softened) # Returning a list of geom_polygon's
}
```

## 2.5 Plot & save!

```{r}
df <- tibble(
  base_gon    = 8,
  base_jutt   = 3,
  n_layer     = 100,
  post_jutt   = 5,
  alpha       = 0.02,
  pol_fill    = "#eb7500",
  seed        = sample(1:1000, size = 3),
  start_x     = 0,
  start_y     = seq(20, 40, length.out = 3)
)
hi <- df %>%
  pmap(soften_edges)

for(item in hi) {
  p_ <- p_ + item
}

p_ <- p_ +
  coord_equal(xlim = c(-10, 10), y = c(10, 50)) +
  theme_void() +
  theme(
    plot.background = element_rect(fill = "#eaebe4", color = "#eaebe4"),
    legend.position = "none"
  )

ggsave(
  here::here("week02", "final.png"),
  p_,
  device    = ragg::agg_png,
  res       = 300,
  units     = "in", # TY everyone in this thread! https://github.com/tidyverse/ggplot2/issues/4347
  width     = 3000, # this is ACTUALLY pixels
  height    = 3000, # also pixels
  limitsize = FALSE # because ggplot2 thinks it's inches
)
```









