---
title: "Untitled"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(rlang)
```

1. We're going to make a kite-like shape, by protruding off the hypotenuse of a right angle triangle. Then plot the eyes and smile

2. We rotate everything randomly, to breathe more life in. I did this with matrix multiplication. To make this rotating work with all the shapes (polygon, eyes, tail), I wrote some helper functions

- `get_mids()` 
- `get_original_location()` 
- `get_centroid_mat()` 
- `rotate_mat()`

This page summarizes what I'm doing: https://math.stackexchange.com/questions/1917449/rotate-polygon-around-center-and-get-the-coordinates/1917485

```{r}
draw_stingrays <- function(start_x, 
                           start_y, 
                           square_len = 0.7, 
                           hyp_prop   = 0.5,
                           prot_amt   = 0.3,
                           rotate_angle) {
  
  # Linear interpolation between two points (hypotenuse) ------------------------------------------------------
  
  right_angle <- atan2(start_y - start_y+square_len, start_x+square_len - start_x) # Just need to use this again lol
  
  get_mids <- function(hyp, square_len_offset) {
    mid_x <- (1-hyp) * (start_x)            + hyp * (start_x+square_len)
    mid_y <- (1-hyp) * (start_y+square_len) + hyp * (start_y)
    
    mid_x_mod <- mid_x + cos(right_angle)*prot_amt*square_len*square_len_offset           
    mid_y_mod <- mid_y + sin(right_angle)*prot_amt*square_len*square_len_offset
    
    list(
      "x" = mid_x_mod,
      "y" = mid_y_mod
    )
  }
  
  
  
  
  
  # vertices matrix that represents the coords of the original shapes ----------------------------------------
  
  get_original_location <- function(n, ...) {
    dots <- enquos(...)
    my_data <- map_dbl(dots, eval_tidy) # I just presented this chapter!
    
    matrix(data = my_data, nrow = 2, ncol = n, byrow = TRUE)
  }
  
  
  
  
  
  # Centroid of the shapes, to rotate around ----------------------------------------------------------------
  
  get_centroid_mat <- function(mat) {
    my_mat <- matrix(data = c(mean(mat[1, ]), 
                              mean(mat[2, ])),
                     nrow = 2,
                     ncol = 1)
    
    matrix(data = my_mat, nrow = 2, ncol = ncol(mat))
  }
  
  
  
  
  
  # rotate the original shape around the centroid by a given angle -----------------------------------------
  
  rotate_mat <- function(orig, centroid) {
    rotations <- matrix(data = c(cos(rotate_angle*pi), -sin(rotate_angle*pi), 
                                 sin(rotate_angle*pi),  cos(rotate_angle*pi)),
                        nrow = 2,
                        ncol = 2,
                        byrow = TRUE)
    
    mult_results <- rotations %*% (orig - centroid) + centroid
    
    mult_results <- mult_results %>% 
      t() %>% 
      as_tibble()
    
    names(mult_results) <- c("x", "y")
    
    mult_results %>% 
      mutate(
        group = paste0("start_x->", start_x, "start_y->", start_y, "hyp_prop->", hyp_prop, "prot_amt->", prot_amt),
        clr = sample(letters[1:4], size = 1)
      )
  }
  
  
  
  
  
  # This is the body of a stingray! ------------------------------------------------------------------------
  
  mids_poly <- get_mids(hyp_prop, 1)   
  
  x1 <- start_x                   # Starting vertices (start from the right angle vertex, and go clockwise) 
  x2 <- start_x 
  x3 <- mids_poly[["x"]] 
  x4 <- start_x + square_len
  
  y1 <- start_y 
  y2 <- start_y + square_len
  y3 <- mids_poly[["y"]]
  y4 <- start_y
  
  orig_loc_polygons <- get_original_location(n = 4, x1, x2, x3, x4, y1, y2, y3, y4)
  centroid_polygons <- get_centroid_mat(mat = orig_loc_polygons)
  res_polygons <- rotate_mat(orig = orig_loc_polygons, centroid = centroid_polygons)
  
  
  
  
  
  # These are the eyes of a stingray! ----------------------------------------------------------------------
  
  eye_locs <- list(hyp_prop - 0.1, hyp_prop + 0.1)
  
  eyes <- eye_locs %>%
    map(get_mids, square_len_offset = 0.4)
  
  orig_loc_eyes <- get_original_location(n = 2, 
                                         transpose(eyes)$x[[1]], transpose(eyes)$x[[2]], 
                                         transpose(eyes)$y[[1]], transpose(eyes)$y[[2]])
  centroid_eyes <- centroid_polygons[, 1:2] # using the polygon's center to rotate
  res_eyes <- rotate_mat(orig = orig_loc_eyes, centroid = centroid_eyes)
  
  
  
  
  
  # This is the smile of a stingray! ----------------------------------------------------------------------
  
  smile_n <- 100
  
  smile_loc <- tibble(
    id = 1:smile_n,
    angle  = (id/smile_n * pi) + right_angle * 3,
    x = (cos(angle) * 0.1 + centroid_polygons[1, 1]),
    y = (sin(angle) * 0.1 + centroid_polygons[2, 1])
  ) 
  
  orig_smile_loc <- matrix(c(smile_loc$x, smile_loc$y), nrow = 2, ncol = nrow(smile_loc), byrow = TRUE)
  centroid_smile <- matrix(data = centroid_polygons[, 1], nrow = 2, ncol = ncol(orig_smile_loc)) # using the polygon's center to rotate
  res_smile <- rotate_mat(orig = orig_smile_loc, centroid = centroid_smile)
  
  
  
  
  
  # Final output! -----------------------------------------------------------------------------------------
  list(
    "polys" = res_polygons,
    "eyes" = res_eyes,
    "smile" = res_smile
  )
}

my_clrs <-c("#FFAE00", "#008E9E", "#004E9D", "#F28973")

helper_func <- function(num_xy) {
  
  poplygon_parameters <- crossing(
    start_x = 1:num_xy,
    start_y = 1:num_xy
  ) %>% 
  mutate(rotate_angle = runif(n = nrow(.), min = -1, max = 1))
  
  poplygon_parameters %>% 
    pmap(draw_stingrays)
}
```

```{r}
res_df1 <- helper_func(num_xy = 5)
polygons <- res_df1 %>% map_dfr("polys")
eyes <- res_df1 %>% map_dfr("eyes")
smile <- res_df1 %>% map_dfr("smile")

g <- ggplot() +
  geom_polygon(data = polygons, aes(x, y, group = group, fill = clr)) +
  geom_point(data = eyes, aes(x, y), size = 4) +
  geom_point(data = smile, aes(x, y)) +
  coord_equal() +
  scale_fill_manual(values = my_clrs) +
  theme_void() +
  theme(
    legend.position = "none",
    plot.background = element_rect(fill = "#909586", color = "#909586")
  )

g

ggsave(
  here::here("week04", "good-copy.png"),
  plot      = g,
  device    = ragg::agg_png,
  res       = 300,
  units     = "in", 
  width     = 3000, 
  height    = 3000, 
  limitsize = FALSE 
)
```

